Numerical investigation of viscous flow instabilities through heterogeneous porous media. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.

### 2017-12-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

\medskip
%Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes. 
Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes. A comprehensive review of mechanisms of fluid instabilities (\ie fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. 
The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, \eg Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}, whereas macroscopic instabilities involve two-phase flow systems \citep{bottoni_1992}. This paper focuses on microscopic instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or \textit{viscous fingering}, Section \ref{section:ViscousInstabilities}).

>>>>

\medskip
%Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes. 
Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes. A comprehensive review of force balance at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}. Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities][]{saffman_1959}. This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or \textit{viscous fingering}, Section \ref{section:ViscousInstabilities}).

% \citet{adler_1988} described both microscopic- and macroscopic-scale instabilities in Darcy flows. Microscopic instabilities describe phenomena occurring locally \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities][]{saffman_1959}
% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. 
%The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, \eg Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}, whereas macroscopic instabilities involve two-phase flow systems \citep{bottoni_1992}. This paper focuses on microscopic instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or \textit{viscous fingering}, Section \ref{section:ViscousInstabilities}).
